Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-05-31 docs/paper/paper.Rmd
update renv
add missing patchwork

```{r packages}
library(data.table)
library(scoringutils)
library(ggplot2)
library(scales)
library(here)
```

```{r load-functions}
source(here("R", "utils.R"))
source(here("R","coverage-plots.R"))
```

>>>>

```{r packages}
library(data.table)
library(scoringutils)
library(ggplot2)
library(patchwork)
library(scales)
library(here)
```

```{r load-functions}
source(here("R", "utils.R"))
source(here("R", "coverage-plots.R"))
```
